Meta-analysis

### 2019-10-23 02_Weather.Rmd
Moved year.day function to it's own R file and referenced with source. I used this function in other chapters

# function to extract date from the year
# format should be Universal time format
year.day <- function(date) {
   if (is.na(date) == TRUE) {
      return(NA)
   } else {
      return(as.numeric(as.Date(date) - as.Date(paste0(
         substr(date, start = 1, stop = 4), "-01-01"
      ))))
   }
}

@@

# Add columns for Year and date to data
war_Tm_aver <- war_Tm_aver %>%
   mutate(
      Year = substr(war_Tm_aver$date, start = 1, stop = 4),
      Day = year.day(war_Tm_aver$date)
   )

# Create data subset of powdery mildew data means for the first sign of the disease by location
Herm_FS <- PM.dat %>%
   group_by(Trial_ref, Location, Year) %>%
   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
   filter(Location == "Hermitage") %>%
   mutate(Day = year.day(First_sign))

@@

# Add columns for Year and date to data
Gat_Tm_aver <- Gat_Tm_aver %>%
   mutate(
      Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
      Day = year.day(Gat_Tm_aver$date)
   )

# Create data subset of powdery mildew data means for the first sign of the disease by location
Gatton_FS <- PM.dat %>%
   group_by(Trial_ref, Location) %>%
   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
   filter(Location == "Gatton") %>%
   mutate(Year = factor(substr(First_sign, 1, 4)),
          Day = year.day(First_sign))

>>>>

# function to extract date from the year
# format should be Universal time format
source("R/year2day.r")

@@

# Add columns for Year and date to data
war_Tm_aver <- war_Tm_aver %>%
   mutate(
      Year = substr(war_Tm_aver$date, start = 1, stop = 4),
      Day = year2day(war_Tm_aver$date)
   )

# Create data subset of powdery mildew data means for the first sign of the disease by location
Herm_FS <- PM.dat %>%
   group_by(Trial_ref, Location, Year) %>%
   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
   filter(Location == "Hermitage") %>%
   mutate(Day = year2day(First_sign))

@@

# Add columns for Year and date to data
Gat_Tm_aver <- Gat_Tm_aver %>%
   mutate(
      Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
      Day = year2day(Gat_Tm_aver$date)
   )

# Create data subset of powdery mildew data means for the first sign of the disease by location
Gatton_FS <- PM.dat %>%
   group_by(Trial_ref, Location) %>%
   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
   filter(Location == "Gatton") %>%
   mutate(Year = factor(substr(First_sign, 1, 4)),
          Day = year2day(First_sign))
